Automated Metadata Generation for Biological Specimen Image Collections

### 2021-02-18 paper/sample-acmsmall-conf.tex
Testing

\documentclass[acmsmall,screen,review]{acmart}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

@@

\section{Introduction}
Text
\section{Background}
Text
\subsection{Related Work}
Text
\section{Objectives}
Text
\section{Data Analysis}
Text
\section{Discussion}
Text
\section{Conclusion}
Text

@@

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

>>>>

%\documentclass[acmsmall,screen,review]{acmart}
\documentclass[acmconf,screen,review]{acmart}
\usepackage{todonotes}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear\todo{test} and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

@@

\section{Introduction}
Text~\ref{demo-intro}~\todo{Liney}
\section{Background}
Text~\todo[noline]{Do this}
\subsection{Related Work}
Text
\section{Objectives}
Text
\section{Data Analysis}
Text
\section{Discussion}
Text \textit{texty text}~\cite{Lamport:LaTeX}
\section{Conclusion}
Text \textbf{text}

@@

\section{Introduction}~\label{demo-intro}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.
